---
title: "Carrying Out a Folder Analysis Using FastTrackR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Carrying Out a Folder Analysis Using FastTrackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load the `fasttrackr` R package. 

```{r setup}
library(fasttrackr)
```

And change the working directory to wherever you would like all your output files to be. 

```{r analysis, eval=FALSE}
## change to working directory
setwd("C:/myworkingdirectory/")
```

For this example I am going to use the example wav and TextGrid files included in Fast TrackR. I am going to write these out to the working directory so that the analysis will be just like one carried out using local wav and TextGrid files.  

```{r, eval=FALSE}
wav_example
tuneR::writeWave(wav_example, "rainbowpassage.wav")

textgrid_example[1:10]
writeLines(textgrid_example, "rainbowpassage.TextGrid")
```

Then I extract the stressed vowels from the recording, using the TextGrid. The output of the extraction is saved in RDS files to the working directory. 

```{r, eval=FALSE}
extractvowels ("rainbowpassage.TextGrid", "rainbowpassage.wav", segmenttier=2,wordtier=1,stress = 1)
```

The formant tracking function relies on the RDS files in the working directory created in the previous step, although they can also be provided directly to the function. 

```{r, eval=FALSE}
formants = trackformants.folder (from = 4500, to = 6500, nsteps = 20)
```

Next, we select the best analysis for each file, again relying on the RDS files in the working directory. 

```{r, eval=FALSE}
selectioninfo = autoselect.classic()
```

After picking the best analysis, we get the winning analyses.

```{r, eval=FALSE}
ff_data = getwinners()
```

Finally, we aggregate the data.

```{r, eval=FALSE}
aggregated = aggregatedata (csvs = ff_data)
```

We can plot the aggregated data. 

```{r, eval=FALSE}
par (mfrow = c(1,1), mar = c(4,4,1,1))
ft.lines(aggregated, xformant=2,yformant=1, revaxes = TRUE, logaxes=FALSE)
ft.arrows(aggregated, xformant=2,yformant=1, revaxes = TRUE, logaxes=FALSE)
ft.points(aggregated, xformant=2,yformant=1, revaxes = TRUE, logaxes=FALSE)
```

And make figures of the competing analyses or of the winning analysis. 

```{r, eval=FALSE}
makecomparisonplots()
makewinnerplots(csvs = ff_data)
```





